\chapter{Organization}

In order to achieve our project on schedule we had to define steps to optimize the management of our time and to avoid delay on deadline.
\paragraph{Step 1}
During early months at the launch of project, we started by writing the user requirements, which is a document etablished according to the need of the product owner. The user requirements allowing all users to orient the project progress and to keep in view the expected objectives. So this is a writing task. This  user requirements was presented to the product owner and before an academic jury.
This was about getting validation on user requirements of the product owner so that we make sure that his needs are clearly understood by us.
\paragraph{}
Then we had, thanks to Mister Chatelier's training a project manangement system called scrum. This system was about detailling all the tasks there was to complete and specifically the sprints.


\paragraph{Step 2}

Thanks to the training given by Mister Christian Chatellier, we achieved the implementation of the project management system. This system includes the backlog writing which listseach individual task there is to complete during the project and affords us to define every sprints (knowing that a sprint represents a week of work). Obvisoulsy, a Trello account was created from that document to allow us to hold a daily project meeting whiwh lasts fifteen minute and is called Scrum. Scrum is useful for daily monitoring of the current sprint.

The main purpose of this organization was for us to complete a second important task which is the writing of the state of art. A document reporting the theoretical aspect to be developped in the project but also the explanation of the methods used and the algorithms to be programmed. This task was carried out throughout the sprint 1.
And at the sprint 2, we did a literature search to deepen the appearance of algorithmic methods and presented the results of our research so that we all stand on the same point of view.

\paragraph{Step 3}
Once, an organization detailling progressively every single task there is to complete and the different actor on it we could more easily work on the programming part of our project to program the prototypes.